Universal algebra and the \texorpdfstring{$ \lambda $}{lambda}-calculus

### 2024-05-28 report/src/paper.tex
Change to the TU Delft PL template

  By Scott's representation theorem, we have $ \varphi_n: \R(U^n, U) \xrightarrow \sim L_n, $ given by
  \[ \varphi_n(f) = \iota_{0, n}(f) ((((c, x_1), x_2), \dots), x_n). \]
  Restricting this equivalence to the morphisms to $ A $ yields
  \[ \R(U^n, A) \cong \{ a : L_n \mid A a = a \}. \]
  Of course, this is natural in $ A $, since for $ g: \R(A, B) $, postcomposing elements of $ \R(U^n, A) $ by $ g $ is equivalent to applying $ g $ to the elements of $ \{ a : L_n \mid A a = a \} $.

@@

Recall that $ \Pshf L $ is isomorphic to the presheaf category $ P \mathbf L $, so it is an elementary topos, so it is locally cartesian closed (Example 5.2.5 and Theorem 5.8.4, \cite{borceux}, Volume 3). Therefore, for a morphism $ f: \Pshf L(Y, X) $, we have adjunctions
\begin{center}
  \begin{tikzcd}
    (\Pshf L \downarrow X) \arrow[r, "f^*"' description, ""{name=B}] & (\Pshf L \downarrow Y) \arrow[l, bend right, "{\sum_f = - \cdot f}"'{name=A}] \arrow[l, bend left, "\prod_f"{name=C}]
    \arrow[from=A, to=B, symbol=\dashv]
    \arrow[from=B, to=C, symbol=\dashv]
  \end{tikzcd}
\end{center}

@@

  Recall that we have a weak equivalence $ \varphi : \R \xrightarrow \sim \hat \R $ (Lemma \ref{lem:retracts-rezk}) and one can imagine that we can extend this to weak equivalences $ \psi_X : (\R \downarrow_D X) \xrightarrow \sim (\hat \R \downarrow_D \varphi(X)) $. Hyland notes that for $ X : \hat \R $, $ \R(\varphi(X)) $ is equivalent to $ (\hat \R \downarrow_D \varphi(X)) $. Implicitly, for $ f: \R(X, Y) $, he wants to lift the functors $ \sum_f $, $ f^* $ and $ \prod_f $ along the equivalences $ \psi $:
  \begin{center}
    \begin{tikzcd}[column sep = .5in, row sep = .5in]
      (\R \downarrow_D X)
        \arrow[d, "\psi_X"]
        \arrow[r, dashed, bend left, "\sum_f"']
        \arrow[r, dashed, bend right, "\prod_f"]
      & (\R \downarrow_D Y)
        \arrow[d, "\psi_Y"]
        \arrow[l, dashed, "f^*" description]\\
      \R(\varphi(X))
        \arrow[r, bend left, "\sum_{\varphi(f)}"']
        \arrow[r, bend right, "\prod_{\varphi(f)}"]
      & \R(\varphi(Y))
        \arrow[l, "\varphi(f)^*" description]\\
    \end{tikzcd}
  \end{center}
  For this to work, we need to turn the weak equivalences $ \psi_X $ into adjoint equivalences. In particular, we know that for every object $ A : \R(\varphi(X)) $, there merely exists a preimage $ \bar A : (\R \downarrow_D X) $ such that $ \psi_X(\bar A) \cong A $, and we need to construct a functor $ \psi_X^{-1}: \R(\varphi(X)) \to (\R \downarrow_D X) $.

@@

  However, as mentioned in \cite{univalent-categories} halfway through the introduction, and as explained more thoroughly in \cite{hottbook}, Lemma 3.8.5, if $ \R(\varphi(X)) $ is not a set (and if $ L $ is nontrivial, it is never a set), then there is no axiom of choice which can turn the `for all \dots, there exists \dots' into a `there exists a function'.

@@

\begin{lemma}\label{lem:elementary-essentially-surjective}
  We have a $ \Lambda $-algebra isomorphism $ \epsilon_A : E_{\R_A}(U)_0 \xrightarrow \sim A $.
\end{lemma}
\begin{proof}
  Take $ c_n = (\lambda x_{n + 1}, x_{n + 1}): \Lambda_n $. Note that
  \[ E(U)_0 = \{ f : A \mid (\lambda x_2, x_1 c_2) \bullet f = f \}. \]
  Therefore, we have a bijection given by
  \[ \epsilon(a) = (x_1 c_1) \bullet a \quad \text{and} \quad \epsilon^{-1}(a) = (\lambda x_2, x_1) \bullet a. \]
  Now, to show that this is an isomorphism of $ \Lambda $-algebras, recall that $ \bullet: \R_A(U^n, U) \times \R_A(I, U)^n \to \R_A(U) $ is given by precomposition with the product morphism and that the $ \Lambda $-algebra structure on $ E(U)_0 $ is given by the embedding of $ \Lambda $ into $ E(U)_0 $, given by $ f \mapsto {\iota_\Lambda}_n(f) \bullet_A () $ for some collection $ ({\iota_\Lambda}_n: \Lambda_n \to \Lambda_0)_n $ (from now on, we will drop the $ n $ and just write $ \iota_\Lambda $). We have for all $ f: \Lambda_n $, and all $ a : E(U)_0^n $,
  \begin{align*}
    \epsilon(f \bullet_{E(U)} a)
    &= ((\iota_\Lambda(f) \bullet_A ()) \circ \langle a_1, \dots, a_n \rangle)(c_n)\\
    &= (\iota_{0, n}(\iota_\Lambda(f)) ((\dots((c_n, x_1 c_n), x_2 c_n), \dots), x_n c_n)) \bullet_A a\\
    &= (\iota_{0, n}(\iota_\Lambda(f)) ((\dots((c_n, x_1), x_2), \dots), x_n)) \bullet_A (\epsilon(a_i))_i,
  \end{align*}
  and we want this to equal $ f \bullet_A (\epsilon(a_i))_i $. Writing $ \bar x_n $ for $ ((\dots((c_n, x_1), x_2), \dots), x_n) $, and leaving out the $ \iota_{0, n} $, all we need to do is show that for all $ f: \Lambda_n $, we have $ \iota_\Lambda(f) \bar x_n = f $. We will do this by structural induction on $ f $.
  \begin{itemize}
    \item If $ f = x_{n, i} $, we have $ \iota_\Lambda(f) = \pi_2 \circ \underbrace{\pi_1 \circ \dots \circ \pi_1}_{n - i} $, and
      \[ \iota_\Lambda(f) \bar x_n = (\pi_2 \circ \pi_1 \circ \dots \circ \pi_1) \bar x_n = x_{n, i}. \]
    \item If $ f = \lambda x_{n + 1}, g $ for some $ g: \Lambda_{n + 1} $, we have
      \[ \iota_\Lambda(f) = (\lambda x_1 x_2, \iota_{0, 2}(\iota_\Lambda(g)) (x_1, x_2)), \]
      and if the induction hypothesis holds for $ g $, then
      \begin{align*}
        \iota_\Lambda(f) \bar x_n
        &= (\lambda x_{n + 1} x_{n + 2}, \iota_\Lambda(g) (x_{n + 1}, x_{n + 2})) \bar x_n\\
        &= \lambda x_{n + 1}, \iota_\Lambda(g) (\bar x_n, x_{n + 1})\\
        &= \lambda x_{n + 1}, g.
      \end{align*}
    \item Recall that application in a $ \lambda $-theory is given by $ g_1 g_2 = \rho(g_1) \bullet (x_1, \dots, x_n, g_2) $. Now, if $ f = g_1 g_2 $ for $ g_1, g_2 : \Lambda_{n + 1} $, we have
      \[
        \iota_\Lambda(f)
        = (\lambda x_1, \iota_\Lambda(g_1) (\pi_1 x_1) (\pi_2 x_1)) \circ \langle \id{U^n}, \iota_\Lambda(g_2) \rangle
        = \lambda x_1, \iota_\Lambda(g_1) x_1 (\iota_\Lambda(g_2) x_1),
      \]
      and if the induction hypothesis holds for $ g_1 $ and $ g_2 $, then
      \begin{align*}
        \iota_\Lambda(f) \bar x_n
        &= (\lambda x_{n + 1}, \iota_\Lambda(g_1) x_{n + 1} (\iota_\Lambda(g_2) x_{n + 1})) \bar x_n\\
        &= \iota_\Lambda(g_1) \bar x_n (\iota_\Lambda(g_2) \bar x_n)\\
        &= g_1 g_2.
      \end{align*}
  \end{itemize}
\end{proof}

Now, take a morphism $ F: \Alg{\Lambda}(A, B) $. Recall that $ \circ $, the categories $ \mathbf R_A $ and $ \mathbf R_B $, and their products and exponential objects are given using $ f \bullet (a_1, \dots, a_n) $ for some $ f: \Lambda_n $ and $ a_1, \dots, a_n : A $. Since we have $ F(f \bullet (a_1, \dots, a_n)) = f \bullet (F(a_1), \dots, F(a_n)) $, $ F $ gives a functor $ F: \R_A \to \R_B $, such that
\[ F(I) = I, F(U) = U, F(A \times B) = F(A) \times F(B) \quad \text{and} \quad F(A^B) = F(A)^{F(B)}, \]
and the same for the product projections and the the natural isomorphisms $ \R_A(C, B^A) \cong \R_A(C \times A, B) $. In particular, we have for all $ f: \R_A(U^n, U) $,
\[ F(f) : \R_B(F(U^n), F(U)) = \R_B(U^n, U). \]
Therefore, $ F $ gives a $ \Lambda $-theory morphism between the endomorphism theories of $ U: \R_A $ and $ U: \R_B $. This allows us to show:
\begin{lemma}\label{lem:elementary-full}
  The functor is full.
\end{lemma}
\begin{proof}
  For any $ \lambda $-theory $ L $, Theorem \ref{thm:Scott} gives an isomorphism of $ \lambda $-theories $ \eta_L: L \xrightarrow \sim E_{\R_{L_0}}(U) $, with
  \[ {\eta_L}_0(f) = \lambda x_1, \iota_{0, 1}(f) \quad \text{and} \quad {\eta_L^{-1}}_0(g) = g(\lambda x_1, x_1). \]

@@

By Lemma 3.2 in \cite{nlab:adjoint_equivalence} and Lemma \ref{lem:zigzag}, $ \eta $ and $ \epsilon $ satisfy both zigazg identities, and we can state the fundamental theorem of the $ \lambda $-calculus:
\begin{theorem}
  There is an adjoint equivalence $ \LamTh \cong \Alg{\Lambda} $, sending a $ \lambda $-theory $ L $ to the $ \Lambda $-algebra $ L_0 $, with an inverse functor that sends a $ \Lambda $-algebra $ A $ to the theory $ E_{\RAct{A_1}}(U_A) $.
\end{theorem}

@@

  The natural isomorphism $ \epsilon_A: A_0 \to A $ is just $ \id A $. Also, $ {\eta_L}_n : L_n \to (L_0)_n $ is given by $ \lambda^n $, with $ \rho^n $ as its inverse. The zigzag identities are trivial, so this gives another, very elemental proof of the fundamental theorem.
  % \begin{align*}
  %   \psi^{-1}(\psi(f))(b)
  %   &= (\lambda x_{n + 2}, x_1 (x_2 x_{n + 2}) \dots (x_{n + 1} x_{n + 2})) \bullet (\psi(f), b_1, \dots, b_n)\\
  %   &= (\lambda x_{n + 2}, x_1 (x_2 x_{n + 2}, \dots, x_{n + 1} x_{n + 2})) \bullet (f (\pi_1, \dots, \pi_n), b_1, \dots, b_n)\\
  %   &= (x_1 \circ \langle x_2, \dots, x_{n + 1} \rangle) \bullet (f (\pi_1, \dots, \pi_n), b_1, \dots, b_n)\\
  %   &= f (\pi_1, \dots, \pi_n) \circ \langle b_1, \dots, b_n \rangle\\
  %   &= f (\pi_1 \circ \langle b_1, \dots, b_n \rangle, \dots, \pi_n \circ \langle b_1, \dots, b_n \rangle)\\
  %   &= f (b_1, \dots, b_n).
  % \end{align*}
  % \begin{align*}
  %   \psi(\psi^{-1}(g))
  %   &= (\lambda x_2 \dots x_{n + 1}, x_1 (x_2, \dots, x_{n + 1})) \bullet ((\lambda x_{n + 2}, x_1 (x_2 x_{n + 2}) \dots (x_{n + 1} x_{n + 2})) \bullet (g, \pi_1, \dots, \pi_n))\\
  %   &= (\lambda x_2 \dots x_{n + 1}, x_1 x_2 \dots x_{n + 1}) \bullet g\\
  %   &= g.
  % \end{align*}
\end{remark}

>>>>

  By Scott's representation theorem, we have $ \varphi_n: \R(U^n, U) \xrightarrow \sim L_n, $ given by
  \[ \varphi_n(f) = \iota_{0, n}(f) (x_i)_i. \]
  Restricting this equivalence to the morphisms to $ A $ yields
  \[ \R(U^n, A) \cong \{ a : L_n \mid A a = a \}. \]
  Of course, this is natural in $ A $, since for $ g: \R(A, B) $, postcomposing elements of $ \R(U^n, A) $ by $ g $ is equivalent to applying $ g $ to the elements of $ \{ a : L_n \mid A a = a \} $.

@@

Recall that $ \Pshf L $ is isomorphic to the presheaf category $ P \mathbf L $, so it is an elementary topos, so it is locally cartesian closed (Example 5.2.5 and Theorem 5.8.4, \textcite{borceux}, Volume 3). Therefore, for a morphism $ f: \Pshf L(Y, X) $, we have adjunctions
\begin{center}
  \begin{tikzcd}
    (\Pshf L \downarrow X) \arrow[r, "f^*"' description, ""{name=B}] & (\Pshf L \downarrow Y) \arrow[l, bend right, "{\sum_f = - \cdot f}"'{name=A}] \arrow[l, bend left, "\prod_f"{name=C}]
    \arrow[from=A, to=B, symbol=\dashv]
    \arrow[from=B, to=C, symbol=\dashv]
  \end{tikzcd}
\end{center}

@@

  Recall that we have a weak equivalence $ \varphi : \R \xrightarrow \sim \hat \R $ (Lemma \ref{lem:retracts-rezk}) and one can imagine that we can extend this to weak equivalences $ \psi_X : (\R \downarrow_D X) \xrightarrow \sim (\hat \R \downarrow_D \varphi(X)) $. Hyland notes that for $ X : \hat \R $, $ \R(\varphi(X)) $ is equivalent to $ (\hat \R \downarrow_D \varphi(X)) $. Implicitly, for $ f: \R(X, Y) $, he wants to lift the functors $ \sum_f $, $ f^* $ and $ \prod_f $ along the equivalences $ \psi $:
  \begin{center}
    \begin{tikzcd}[sep=large]
      (\R \downarrow_D X)
        \arrow[d, "\psi_X"]
        \arrow[r, dashed, bend left, "\sum_f"']
        \arrow[r, dashed, bend right, "\prod_f"]
      & (\R \downarrow_D Y)
        \arrow[d, "\psi_Y"]
        \arrow[l, dashed, "f^*" description]\\
      \R(\varphi(X))
        \arrow[r, bend left, "\sum_{\varphi(f)}"']
        \arrow[r, bend right, "\prod_{\varphi(f)}"]
      & \R(\varphi(Y))
        \arrow[l, "\varphi(f)^*" description]\\
    \end{tikzcd}
  \end{center}
  For this to work, we need to turn the weak equivalences $ \psi_X $ into adjoint equivalences. In particular, we know that for every object $ A : \R(\varphi(X)) $, there merely exists a preimage $ \bar A : (\R \downarrow_D X) $ such that $ \psi_X(\bar A) \cong A $, and we need to construct a functor $ \psi_X^{-1}: \R(\varphi(X)) \to (\R \downarrow_D X) $.

@@

  However, as mentioned in \textcite{univalent-categories} halfway through the introduction, and as explained more thoroughly in \textcite{hottbook}, Lemma 3.8.5, if $ \R(\varphi(X)) $ is not a set (and if $ L $ is nontrivial, it is never a set), then there is no axiom of choice which can turn the `for all \dots, there exists \dots' into a `there exists a function'.

@@

\begin{lemma}\label{lem:elementary-essentially-surjective}
  We have a $ \Lambda $-algebra isomorphism $ \epsilon_A : E_{\R_A}(U)_0 \xrightarrow \sim A $.
\end{lemma}
\begin{proof}
  Take $ c_n = (\lambda x_{n + 1}, x_{n + 1}): \Lambda_n $. Note that
  \[ E(U)_0 = \{ f : A \mid (\lambda x_2, x_1 c_2) \bullet f = f \}. \]
  Therefore, we have a bijection given by
  \[ \epsilon(a) = (x_1 c_1) \bullet a \quad \text{and} \quad \epsilon^{-1}(a) = (\lambda x_2, x_1) \bullet a. \]
  Now, to show that this is an isomorphism of $ \Lambda $-algebras, recall that $ \bullet: \R_A(U^n, U) \times \R_A(I, U)^n \to \R_A(U) $ is given by precomposition with the product morphism and that the $ \Lambda $-algebra structure on $ E(U)_0 $ is given by the embedding of $ \Lambda $ into $ E(U)_0 $, given by $ f \mapsto {\iota_\Lambda}_n(f) \bullet_A () $ for some collection $ ({\iota_\Lambda}_n: \Lambda_n \to \Lambda_0)_n $ (from now on, we will drop the $ n $ and just write $ \iota_\Lambda $). We have for all $ f: \Lambda_n $, and all $ a : E(U)_0^n $,
  \begin{align*}
    \epsilon(f \bullet_{E(U)} a)
    &= ((\iota_\Lambda(f) \bullet_A ()) \circ \langle a_i \rangle_i)(c_n)\\
    &= (\iota_{0, n}(\iota_\Lambda(f)) (x_i c_n)_i) \bullet_A a\\
    &= (\iota_{0, n}(\iota_\Lambda(f)) (x_i)_i) \bullet_A (\epsilon(a_i))_i,
  \end{align*}
  and we want this to equal $ f \bullet_A (\epsilon(a_i))_i $. Leaving out the $ \iota_{0, n} $, all we need to do is show that for all $ f: \Lambda_n $, we have $ \iota_\Lambda(f) (x_i)_i = f $. We will do this by structural induction on $ f $.
  \begin{itemize}
    \item If $ f = x_{n, i} $, we have $ \iota_\Lambda(f) = \pi_{n, i} $, and
      \[ \iota_\Lambda(f) (x_i)_i = \pi_{n, i} (x_{n, i})_i = x_{n, i}. \]
    \item If $ f = \lambda x_{n + 1}, g $ for some $ g: \Lambda_{n + 1} $, we have
      \[ \iota_\Lambda(f) = (\lambda x_1 x_2, \iota_{0, 2}(\iota_\Lambda(g)) (x_1, x_2)), \]
      and if the induction hypothesis holds for $ g $, then
      \begin{align*}
        \iota_\Lambda(f) (x_i)_i
        &= (\lambda x_{n + 1} x_{n + 2}, \iota_\Lambda(g) (x_{n + 1}, x_{n + 2})) (x_i)_i\\
        &= \lambda x_{n + 1}, \iota_\Lambda(g) ((x_i)_i, x_{n + 1})\\
        &= \lambda x_{n + 1}, g.
      \end{align*}
    \item Recall that application in a $ \lambda $-theory is given by $ g_1 g_2 = \rho(g_1) \bullet (x_1, \dots, x_n, g_2) $. Now, if $ f = g_1 g_2 $ for $ g_1, g_2 : \Lambda_{n + 1} $, we have
      \[
        \iota_\Lambda(f)
        = (\lambda x_1, \iota_\Lambda(g_1) (\pi_1 x_1) (\pi_2 x_1)) \circ \langle \id{U^n}, \iota_\Lambda(g_2) \rangle
        = \lambda x_1, \iota_\Lambda(g_1) x_1 (\iota_\Lambda(g_2) x_1),
      \]
      and if the induction hypothesis holds for $ g_1 $ and $ g_2 $, then
      \begin{align*}
        \iota_\Lambda(f) (x_i)_i
        &= (\lambda x_{n + 1}, \iota_\Lambda(g_1) x_{n + 1} (\iota_\Lambda(g_2) x_{n + 1})) (x_i)_i\\
        &= \iota_\Lambda(g_1) (x_i)_i (\iota_\Lambda(g_2) (x_i)_i)\\
        &= g_1 g_2.
      \end{align*}
  \end{itemize}
\end{proof}

Now, take a morphism $ F: \Alg{\Lambda}(A, B) $. Recall that $ \circ $, the categories $ \mathbf R_A $ and $ \mathbf R_B $, and their products and exponential objects are given using $ f \bullet (a_1, \dots, a_n) $ for some $ f: \Lambda_n $ and $ a_1, \dots, a_n : A $. Since we have $ F(f \bullet (a_i)_i) = f \bullet (F(a_i)) $, $ F $ gives a functor $ F: \R_A \to \R_B $, such that
\[ F(I) = I, F(U) = U, F(A \times B) = F(A) \times F(B) \quad \text{and} \quad F(A^B) = F(A)^{F(B)}, \]
and the same for the product projections and the the natural isomorphisms $ \R_A(C, B^A) \cong \R_A(C \times A, B) $. In particular, we have for all $ f: \R_A(U^n, U) $,
\[ F(f) : \R_B(F(U^n), F(U)) = \R_B(U^n, U). \]
Therefore, $ F $ gives a $ \Lambda $-theory morphism between the endomorphism theories of $ U: \R_A $ and $ U: \R_B $. This allows us to show:
\begin{lemma}\label{lem:elementary-full}
  The functor is full.
\end{lemma}
\begin{proof}
  For any $ \lambda $-theory $ L $, Theorem \ref{thm:Scott} gives an isomorphism of $ \lambda $-theories $ \eta_L: L \xrightarrow \sim E_{\R_{L_0}}(U) $, with
  \[ {\eta_L}_0(f) = \lambda x_1, \iota_{0, 1}(f) \quad \text{and} \quad {\eta_L^{-1}}_0(g) = g(\lambda x_1, x_1). \]

@@

By Lemma 3.2 in \textcite{nlab:adjoint_equivalence} and Lemma \ref{lem:zigzag}, $ \eta $ and $ \epsilon $ satisfy both zigazg identities, and we can state the fundamental theorem of the $ \lambda $-calculus:
\begin{theorem}
  There is an adjoint equivalence $ \LamTh \cong \Alg{\Lambda} $, sending a $ \lambda $-theory $ L $ to the $ \Lambda $-algebra $ L_0 $, with an inverse functor that sends a $ \Lambda $-algebra $ A $ to the theory $ E_{\RAct{A_1}}(U_A) $.
\end{theorem}

@@

  The natural isomorphism $ \epsilon_A: A_0 \to A $ is just $ \id A $. Note that, even though $ A_0 = A $ as sets, their $ \Lambda $-algebra structures are defined differently, so it takes some work to show that $ \epsilon_A $ is a $ \Lambda $-algebra morphism. Also, $ {\eta_L}_n : L_n \to (L_0)_n $ is given by $ \lambda^n $, with $ \rho^n $ as its inverse. The zigzag identities are trivial, so this gives another, very elemental proof of the fundamental theorem.
  % \begin{align*}
  %   \psi^{-1}(\psi(f))(b)
  %   &= (\lambda x_{n + 2}, x_1 (x_2 x_{n + 2}) \dots (x_{n + 1} x_{n + 2})) \bullet (\psi(f), b_1, \dots, b_n)\\
  %   &= (\lambda x_{n + 2}, x_1 (x_2 x_{n + 2}, \dots, x_{n + 1} x_{n + 2})) \bullet (f (\pi_1, \dots, \pi_n), b_1, \dots, b_n)\\
  %   &= (x_1 \circ \langle x_2, \dots, x_{n + 1} \rangle) \bullet (f (\pi_1, \dots, \pi_n), b_1, \dots, b_n)\\
  %   &= f (\pi_1, \dots, \pi_n) \circ \langle b_1, \dots, b_n \rangle\\
  %   &= f (\pi_1 \circ \langle b_1, \dots, b_n \rangle, \dots, \pi_n \circ \langle b_1, \dots, b_n \rangle)\\
  %   &= f (b_1, \dots, b_n).
  % \end{align*}
  % \begin{align*}
  %   \psi(\psi^{-1}(g))
  %   &= (\lambda x_2 \dots x_{n + 1}, x_1 (x_2, \dots, x_{n + 1})) \bullet ((\lambda x_{n + 2}, x_1 (x_2 x_{n + 2}) \dots (x_{n + 1} x_{n + 2})) \bullet (g, \pi_1, \dots, \pi_n))\\
  %   &= (\lambda x_2 \dots x_{n + 1}, x_1 x_2 \dots x_{n + 1}) \bullet g\\
  %   &= g.
  % \end{align*}
\end{remark}
